Regularized target encoding outperforms traditional methods in supervised machine learning with high cardinality features

### 2021-04-30 publication/manuscript.Rmd
fix declarations and dois

### Code Availability
All analysis code is available from \url{https://github.com/compstat-lmu/paper_2021_categorical_feature_encodings}

### Availability of Data
Our analysis code downloads all benchmark datasets from \url{https://www.openml.org/}.

>>>>

### Code Availability
All analysis code is publicly available at \url{https://github.com/compstat-lmu/paper_2021_categorical_feature_encodings}.

### Availability of Data
All benchmark datasets are publicly available at \url{https://www.openml.org/}.
